---
title: "Monolithic Preconditions Report"
author: "DISPLAY Lab"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Performer Tabulation
###  How many performers had an acceptable paver?
Proportion of performers with at least one acceptable paver broken down by month.
Total number of performers is `r n_performers`.
```{r perf_2, echo=FALSE, results='asis'}
df_perf_2 %>% knitr::kable(x=.)
```

### Paver Definition
A paver is bite sized information about the performance annotation of a particular performer, measure, and comparator.
It represents the unit the causal pathways are designed to operate on.
When a performer has an acceptable paver, it means they have annotations about a measure and comparator that satisfies the preconditions of a causal pathway.

\newpage
## Paver Tabulation
#### How many pavers are there?
Number of pavers is the same across all months due to anaylsis method.
All of performers in this data had to have sufficient data to generate one paver.
Performers without sufficient data (denominator < 10 for all measures) were previously excluded.
```{r sum_1, echo=FALSE, results='asis'}
knitr::kable(data.frame("Number of Pavers"=n_candidates, "Number of Performers"=n_performers))
```

####  How many acceptable pavers are there?
```{r candi_1, echo=FALSE, results='asis'}
knitr::kable(df_candi_1)
```

####  How many pavers did each causal pathway accept?
```{r path_1, echo=FALSE, results='asis'}
df_path_1 %>% select(1:4) %>% knitr::kable(x=.)
df_path_1 %>% select(c(1,5:7)) %>% knitr::kable(x=.)
```

###  How many pavers per performer?
NOTE: Uniform avg number of pavers is artifact of having an annotation (e.g. comparator type) always be applicable.
This means what is counted here is the number of measures-comparators for which sufficient data is was available.
```{r perf_1, echo=FALSE, results='asis'}
df_perf_1 %>% select(1:4) %>% knitr::kable(x=.)
df_perf_1 %>% select(c(1,2,5:7)) %>% knitr::kable(x=.)
```

\newpage
### Annotation tabulation
####  How many times does each annotation appear in the performers?
```{r anno_1, echo=FALSE, results='asis'}
df_anno_1 %>% select(1:4) %>% knitr::kable(x=.)
df_anno_1 %>% select(c(1,5:7)) %>% knitr::kable(x=.)
```

\newpage
## Stepping Back Analysis Method

### Special Annotation
A stepping backwards preconditions analysis is accomplished by way of a special annotation function.
It filters the data back `x` number of months and runs the other annotations that are temporaly dependent.
The annotations that have been run on data with `x` months filtered out are named specially with `_x` appended.
For example, `positive_performance_gap_3` indicates a positive performance gap in the data 3 months back.

### Query After Swapping Annotation IRIS 
Initially the pavers are evaluated by applying causal pathway preconditions and querying the results.
To step back and evaluate what the pavers would have been `x` months ago, the annotations need to be altered to match the IRIs the causal pathways operate on.
This is accomplished by a simple IRI swapping scheme where the standard annotation gets swapped for the equivalent `x-1` special annotation, and the `x` special annotation gets swapped for the standard.

For example, after initial evaluation and query, stepping 1 month back:

1. All instances of `psdo_0000104` changed to `positive_performance_gap_0`
1. All instances of `positive_performance_gap_1` changed to `psdo_0000104`
1. Swapping is also performed for:
    - `psdo_0000105` 
    - `psdo_0000100`
    - `psdo_0000099`
    - `slowmo#Achievement`
1. Existing triples of the form `paver acceptable_by causal_pathway` are deleted removing accepted from the previous IRI set.
1. Causal pathways are applied writing in new `paver acceptable_by causal_pathway` based on the newly swapped IRIs.
1. Summary queres are run and collected into summary file 
